% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=110061]
\definecolor[rulecolor][h=110061]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd, page=no]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle, page=no]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}, page=no]
\setuphead[subsubsection][style=\bf, page=no]

\setuphead[chapter, section, subsection, subsubsection][number=no]

\definemeasure[cslhangindent][1.5em]
\definestartstop
  [cslreferences]
  [before={%
     \setupnarrower[left=\measure{cslhangindent}]
     \startnarrower[left]%
     \setupindenting[-\leftskip,yes,first]%
     \doindentation%
   },
   after=\stopnarrower]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\defineitemgroup[enumerate]
\setupenumerate[each][fit][itemalign=left,distance=.5em,style={\feature[+][default:tnum]}]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]
\setupxtable[frame=off,option={stretch,width}]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext
\startalignment[right]
  \blank[2*big]
  {\tfd Mathias Thibaut Louboutin}
  \blank[3*medium]
  {\tfa \crlf
733 York View Dr, Auburn, 30011, GA\crlf
mathias.louboutin@gmail.com\crlf
404-451-6131\crlf
\useURL[url1][mloubout.github.io]\from[url1]\crlf
\goto{Github}[url(https://github.com/mloubout)]\crlf
\goto{@louboutjunior}[url(https://twitter.com/Louboutjunior)]}
  \blank[3*medium]
\stopalignment

\startsectionlevel[title={Experience},reference={experience}]

\startdescription{March 2023-*}
  {\bf Computational Imaging Scientist}: Oak Ridge National Laboratory,
  Oak Ridge, TN {\em Scientific engagmenent, INCITE }

  {\em Medical Imaging}

  {\em HPC (Frontier, Summit, \ldots{})}
\stopdescription

\startdescription{July 2020-- February 2023}
  {\bf Postdoctoral Fellow}: Georgia Institute of Technology, Atlanta,
  GA

  {\em High performance/low memory randomized linear algebra for
  backpropagation based inverse problems}

  {\em Cloud HPC for separable problems (task parallel)}

  {\em Supervising the PhD and MSc students}

  {\em Managing and developping the software stack for the Lab
  (\goto{slimgroup}[url(https://github.com/slimgroup)])}

  {\em Machine learning for geophysical and medical wave-equation based
  inverse problems}

  {\em HPC for machine learning}

  {\em Geological Carbon Storage seismic monitoring}
\stopdescription

\stopsectionlevel

\startsectionlevel[title={Computational
experience},reference={computational-experience}]

\startdescription{Open Source}
  {\bf \goto{Devito}[url(https://github.com/devitocodes/devito)]}: A
  symbolic domain specific language (DSL) for stencil computation with
  just-in-time compilation and code generation. Achieves state of the
  art performance while providing a high-level mathematical interface to
  the users for the development of stencil based applications.

  {\bf \goto{JUDI}[url(https://github.com/slimgroup/JUDI.jl)]}: Linear
  algebra high level API for wave-equation based inversion. This pacage
  is built on top of Devito to have high performance wave-equation
  solvers. A new additional Azure batch extension was developped for
  scalability
  \goto{JUDI4Cloud}[url(https://github.com/slimgroup/JUDI.jl)].

  {\bf \goto{XConv}[url(https://github.com/slimgroup/XConv)]}: High
  performance low memory convolutional layer. This repository implements
  both in julia (for Flux.jl) and in python (for pytorch) a
  convolutional layer that has virtually a zero memory imprnt for
  training using randomized linear algebra to compute an unbiased
  estimate of the gradient with respect to the weights. Additionaly, a
  byte only implementation of the ReLU layer leads to memry reduction by
  a factor of X2 for full networks.

  {\bf \goto{dfno}[url(https://github.com/slimgroup/dfno)]}: Model
  parallel (MPI model decomposition) implementation of Fourier Neural
  Operators for PyTorch. Extension of distdl, a model parallel extension
  of PyTorch.

  {\bf \goto{InvertibleNetworks.jl}[url(https://github.com/slimgroup/InvertibleNetworks.jl)]}:
  Native Julia implementation of invertible networks for variational
  inference, generative models and normalizing flows.
\stopdescription

\startdescription{Programming Languages}
  {\bf Python:} Main programming language for the development of
  \goto{Devito}[url(https://github.com/devitocodes/devito)] and machine
  learning applications.

  {\bf Julia:} Heavy development of research software at Georgia Tech
  (\goto{slimgroup}[url(https://github.com/slimgroup)]) in Julia

  {\bf docker} Developped and automatized the deployement of
  \goto{Devito}[url(https://github.com/devitocodes/devito)] and
  \goto{JUDI}[url(https://github.com/slimgroup/JUDI.jl)] images through
  CI (github actions).

  Knowledge of {\bf C}, {\bf Linux}, {\bf Bash}, {\bf PyTorch},
  {\bf Azure}, {\bf Latex}, {\bf Markdown}, {\bf Matlab}, {\bf MPI},
  {\bf OPenMP}, {\bf OpenACC}
\stopdescription

\startdescription{HPC}
  {\bf \goto{Devito}[url(https://github.com/devitocodes/devito)]:} Weak
  and strong scaling benchmarks of
  \goto{Devito}[url(https://github.com/devitocodes/devito)] on
  on-premise (Imperical college) and Cloud (Azure) hardware.

  {\bf \goto{JUDI}[url(https://github.com/slimgroup/JUDI.jl)]:}
  Implementation and deployment at scale of
  \goto{JUDI}[url(https://github.com/slimgroup/JUDI.jl)] on clusters and
  Azure Batch (up 300 nodes).

  {\bf Optimum (2015-2018):} Early PhD 50 nodes cluster. Development of
  parallel Matlab seismic inverse problem algorithms (FWI/RTM).

  {\bf YEMOJA (2017-2018):} Part of a collaboration with SENAI-CIMANTEC.
  Scaling of our Matlab and Julia framework to hundred of nodes.

  {\bf Cloud (2018-):} Serverless and clusterless framework for task
  parallel inverse problems on AWS and Azure.

  {\bf Perlmutter (2022-):} Scaling of MPI-parallel Fourier Neural
  Operator on Perlmutter (and previously Summit).
\stopdescription

\stopsectionlevel

\startsectionlevel[title={Education},reference={education}]

\startdescription{2018--2020}
  {\bf PhD, Computer Science}; Georgia Institute of Technology, Atlanta,
  GA

  {\em Thesis title: Modeling for inversion in exploration geophysics}
  \goto{Link}[url(https://slim.gatech.edu/content/modeling-inversion-exploration-geophysics)]

  {\em Numerical and computational methods for large scale simulation
  based inverse problems and machine learning}
\stopdescription

\startdescription{2013--2018}
  {\bf PhD, Earth Science}; University of British Columbia, Canada

  {\em Transfered to Georgia Institute of Technology in January 2018
  following my supervior new position there.}
\stopdescription

\startdescription{2016 Feb-Aug}
  {\bf Visiting PhD, Computer Science}; Impertial College London, UK

  {\em Automatic code generation for geophysical exploration
  applications with finite differences}
\stopdescription

\startdescription{2011--2013}
  {\bf MSc, Applied Mathematics}; Universite de Rennes 1, Rennes, France

  {\em Valedictorian}

  {\em Required coursework}: Calculus, Numerical Methods, PDE
  Resolution, Opti- mization, C/C++ Computing, Mathematics Modeling and
  Simulation, Finite Element Method*

  {\em Elective coursework}: Fluid Mechanics, Continuum Mechanics and
  Thermo- mechanics, Bio-mechanics, Geophysics Modeling*
\stopdescription

\startdescription{2008--2011}
  {\bf BSc, Aeronautical Engineering,} ENSICA-ISAE, Toulouse, France

  {\em Leading French Aeronautical Engineering School.}

  {\em Required coursework}: Mathematics, Mechanics, Continuum
  Mechanics, Struc- tures Mechanics, Signal Processing, Thermodynamics,
  Fluid Mechanics, Java progamming*

  {\em Elective coursework}: Estimation Methods, Earth Observation
  Satellites, Microwaves Processing*
\stopdescription

\startdescription{2006--2008}
  {\bf Classe Preparatoires}; Lycee Chateaubriand, Rennes, France

  {\em Advanced undergraduate preparatory program for national ranking
  entry exam.}
\stopdescription

\stopsectionlevel

\startsectionlevel[title={Internships},reference={internships}]

\startdescription{Summer 2013}
  {\bf Research internship}; ONERA, Toulouse, France

  {\em Scattering patterns of atmospheric dust clouds analysis with the
  Discrete Dipole Approximation (DDA) method.}
\stopdescription

\startdescription{Summer 2012}
  {\bf Research internship}; INRIA, Grenoble, France

  {\em Intern in NANO-D department at INRIA-Grenoble. L2-SVM for protein
  interactions. Runtime and accuracy improvement of the C implementation
  and algorithmic development.}
\stopdescription

\startdescription{Summer 2011}
  {\bf Internship, Aeroconseil}, Toulouse, France

  {\em Developed an interface for aerodynamics calculus in JAVA. Reading
  and implementation of Excel and Scilab scripts through the interface.}
\stopdescription

\stopsectionlevel

\startsectionlevel[title={Additonal
skills},reference={additonal-skills}]

\startitemize
\item
  Languages:

  \startitemize[packed]
  \item
    French (native speaker)
  \item
    English (Advanced, PhD in USA)
  \stopitemize
\item
  Miscelanous CS:

  \startitemize[packed]
  \item
    Linux, Shell script, Latex, Markdown, Github, Unix, Matlab
  \stopitemize
\stopitemize

\stopsectionlevel

\startsectionlevel[title={Publications},reference={publications}]

\startcslreferences

\reference[ref-deaguiar2016SCdff]{}%
Aguiar, M. de, Gorman, G., Herrmann, F. J., Kukreja, N., Lange, M.,
Louboutin, M., & Zacarias, F. V. (2016, November). DeVito: Fast finite
difference computation. Retrieved from
\useURL[url2][https://slim.gatech.edu/Publications/Public/Conferences/SC/2016/deaguiar2016SCdff/deaguiar2016SCdff_poster.pdf]\from[url2]

\reference[ref-bisbas2020IPDPStbf]{}%
Bisbas, G., Luporini, F., Louboutin, M., Nelson, R., Gorman, G., &
Kelly, P. H. J. (2021, May). Temporal blocking of finite-difference
stencil operators with sparse "off-the-grid" sources.
doi:\goto{10.1109/IPDPS49936.2021.00058}[url(https://doi.org/10.1109/IPDPS49936.2021.00058)]

\reference[ref-erdinc2022AAAIdcc]{}%
Erdinc, H. T., Gahlot, A. P., Yin, Z., Louboutin, M., & Herrmann, F. J.
(2022a, November). De-risking carbon capture and sequestration with
explainable CO$_2$ leakage detection in time-lapse seismic monitoring
images. Retrieved from
\useURL[url3][https://slim.gatech.edu/Publications/Public/Conferences/AAAI/2022/erdinc2022AAAIdcc/erdinc2022AAAIdcc.pdf]\from[url3]

\reference[ref-erdinc2022ML4SEISMICdgp]{}%
Erdinc, H. T., Gahlot, A. P., Yin, Z., Louboutin, M., & Herrmann, F. J.
(2022b, November). De-risking GCS projects with explainable CO$_2$
leakage detection in time-lapse seismic images. Retrieved from
\useURL[url4][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2022/erdinc2022ML4SEISMICdgp/index.html]\from[url4]

\reference[ref-gorman2016SINBADFopp]{}%
Gorman, G., Aguiar, M. de, Ham, D., Herrmann, F. J., Kelly, P. H. J.,
Kukreja, N., \ldots{} Zacarias, F. V. (2016). Open performance portablE
SeismiC imaging-OPESCI. SINBAD. Retrieved from
\useURL[url5][https://slim.gatech.edu/Publications/Public/Conferences/SINBAD/2016/Fall/gorman2016SINBADFopp/gorman2016SINBADFopp.pdf]\from[url5]

\reference[ref-herrmann2018SMCtpa]{}%
Herrmann, F. J., Gorman, G. J., Hückelheim, J., Lensink, K., Kelly, P.
H. J., Kukreja, N., \ldots{} Witte, P. A. (2018, August). The power of
abstraction in computational exploration seismology.

\reference[ref-herrmann2019EAGEHPCaii]{}%
Herrmann, F. J., Jones, C., Gorman, G., Hückelheim, J., Lensink, K.,
Kelly, P. H. J., \ldots{} Witte, P. A. (2019, October). Accelerating
ideation and innovation cheaply in the cloud the power of abstraction,
collaboration and reproducibility.

\reference[ref-herrmann2021Microsoftrla]{}%
Herrmann, F. J., Louboutin, M., & Siahkoohi, A. (2021, March). ML@scale
using randomized linear algebra.

\reference[ref-herrmann2021SEGWSlts]{}%
Herrmann, F. J., Louboutin, M., Yin, Z., & Witte, P. A. (2021, October).
Low-cost time-lapse seismic imaging of CCS with the joint recovery
model.

\reference[ref-herrmann2021Delftlwi]{}%
Herrmann, F. J., Siahkoohi, A., Orozco, R., Rizzuti, G., Witte, P. A., &
Louboutin, M. (2021, June). Learned wave-based imaging - variational
inference at scale. Retrieved from
\useURL[url6][https://slim.gatech.edu/Publications/Public/Conferences/Delft/2021/herrmann2021Delftlwi/herrmann2021Delftlwi.pdf]\from[url6]

\reference[ref-grady2022SCtll]{}%
II, T. J. G., Khan, R., Louboutin, M., Yin, Z., Witte, P. A., Chandra,
R., \ldots{} Herrmann, F. J. (2022a, April). {\em Model-parallel fourier
neural operators as learned surrogates for large-scale parametric PDEs}.
Retrieved from
\useURL[url7][https://slim.gatech.edu/Publications/Public/Submitted/2022/grady2022SCtll/grady2022SCtll.pdf]\from[url7]

\reference[ref-grady2022ML4SEISMICesn]{}%
II, T. J. G., Khan, R., Louboutin, M., Yin, Z., Witte, P. A., Chandra,
R., \ldots{} Herrmann, F. J. (2022b, November). Effective scaling of
numerical surrogates via domain-decomposed fourier neural operators.
Retrieved from
\useURL[url8][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2022/grady2022ML4SEISMICesn/index.html]\from[url8]

\reference[ref-kukreja2019PASCccd]{}%
Kukreja, N., Hückelheim, J., Louboutin, M., Hovland, P., & Gorman, G.
(2019). Combining checkpointing and data compression to accelerate
adjoint-based optimization problems. {\em Euro-Par 2019: Parallel
Processing}, 87--100.
doi:\goto{10.1007/978-3-030-29400-7_7}[url(https://doi.org/10.1007/978-3-030-29400-7_7)]

\reference[ref-kukreja2020lcc]{}%
Kukreja, N., Hueckelheim, J., Louboutin, M., Washbourne, J., Kelly, P.
H. J., & Gorman, G. J. (2022). Lossy checkpoint compression in full
waveform inversion. {\em Geoscientific Model Development}, {\em 15}(9),
3815--3829.
doi:\goto{10.5194/gmd-15-3815-2022}[url(https://doi.org/10.5194/gmd-15-3815-2022)]

\reference[ref-kukreja2017SIAMdsm]{}%
Kukreja, N., Lange, M., Louboutin, M., Luporini, F., & Gorman, G.
(2017). Devito: Symbolic math for automated fast finite difference
computations. Retrieved from
\useURL[url9][https://slim.gatech.edu/Publications/Public/Conferences/SIAM/2017/kukreja2017SIAMdsm/kukreja2017SIAMdsm_pres.mov]\from[url9]

\reference[ref-kukreja2016OGHPClsm]{}%
Kukreja, N., Louboutin, M., Lange, M., Luporini, F., & Gorman, G. (2017,
March). Leveraging symbolic math for rapid development of applications
for seismic modeling. Retrieved from
\useURL[url10][https://slim.gatech.edu/Publications/Public/Conferences/OGHPC/2017/kukreja2016OGHPClsm/kukreja2016OGHPClsm.pdf]\from[url10]

\reference[ref-kukreja2016WOLFHPCdaf]{}%
Kukreja, N., Louboutin, M., Zacarias, F. V., Luporini, F., Lange, M., &
Gorman, G. (2016, November). Devito: Automated fast finite difference
computation. Retrieved from
\useURL[url11][https://slim.gatech.edu/Publications/Public/Conferences/SC/2016/WOLFHPC/kukreja2016WOLFHPCdaf/kukreja2016WOLFHPCdaf.pdf]\from[url11]

\reference[ref-lange2016dtg]{}%
Lange, M., Kukreja, N., Louboutin, M., Luporini, F., Zacarias, F. V.,
Pandolfo, V., \ldots{} Gorman, G. (2016, November). Devito: Towards a
generic finite difference DSL using symbolic python.
doi:\goto{10.1109/PyHPC.2016.9}[url(https://doi.org/10.1109/PyHPC.2016.9)]

\reference[ref-lange2017SCIPYofd]{}%
Lange, M., Kukreja, N., Luporini, F., Louboutin, M., Yount, C.,
Hückelheim, J., & Gorman, G. (2017, July). Optimised finite difference
computation from symbolic equations. Retrieved from
\useURL[url12][http://conference.scipy.org/proceedings/scipy2017/michael_lange.html]\from[url12]

\reference[ref-louboutin2020THmfi]{}%
Louboutin, M. (2020, March). {\em Modeling for inversion in exploration
geophysics} (phd). Georgia Institute of Technology, Atlanta. Retrieved
from
\useURL[url13][https://slim.gatech.edu/Publications/Public/Thesis/2020/louboutin2020THmfi/louboutin2020THmfi.pdf]\from[url13]

\reference[ref-louboutin2021ML4SEISMICmos]{}%
Louboutin, M. (2021, November). ML4Seismic open source software
environment. Retrieved from
\useURL[url14][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2021/louboutin2021ML4SEISMICmos/Mon-10-10-Louboutin.pdf]\from[url14]

\reference[ref-louboutin2016SEGocp]{}%
Louboutin, M., Gorman, G., & Herrmann, F. J. (2016). {\em Optimizing the
computational performance and maintainability of time-domain
modelling-leveraging multiple right-hand-sides} (No. TR-EOAS-2016-2).
UBC. Retrieved from
\useURL[url15][https://slim.gatech.edu/Publications/Public/TechReport/2016/louboutin2016SEGocp/louboutin2016SEGocp.html]\from[url15]

\reference[ref-louboutin2016OGHPCocp]{}%
Louboutin, M., Gorman, G., & Herrmann, F. J. (2017). {\em Optimizing the
computational performance of time-domain modelling-leveraging multiple
right-hand-sides} (No. TR-EOAS-2017-2). UBC. Retrieved from
\useURL[url16][https://slim.gatech.edu/Publications/Public/TechReport/2017/louboutin2016OGHPCocp/louboutin2016OGHPCocp.pdf]\from[url16]

\reference[ref-louboutin2017EAGEdns]{}%
Louboutin, M., Guasch, L., & Herrmann, F. J. (2017, June). Data
normalization strategies for full-waveform inversion.
doi:\goto{10.3997/2214-4609.201700720}[url(https://doi.org/10.3997/2214-4609.201700720)]

\reference[ref-louboutin2015SINBADFess]{}%
Louboutin, M., & Herrmann, F. J. (2015a). Extending the search space of
time-domain adjoint-state FWI w/ randomized implicit time shifts.
SINBAD. Retrieved from
\useURL[url17][https://slim.gatech.edu/Publications/Public/Conferences/SINBAD/2015/Fall/louboutin2015SINBADFess/louboutin2015SINBADFess.pdf]\from[url17]

\reference[ref-louboutin2015SEGtcs]{}%
Louboutin, M., & Herrmann, F. J. (2015b, October). Time compressively
sampled full-waveform inversion with stochastic optimization.
doi:\goto{10.1190/segam2015-5924937.1}[url(https://doi.org/10.1190/segam2015-5924937.1)]

\reference[ref-louboutin2016SINBADFhps]{}%
Louboutin, M., & Herrmann, F. J. (2016). High-performance seismic
applications of OPESCI. SINBAD. Retrieved from
\useURL[url18][https://slim.gatech.edu/Publications/Public/Conferences/SINBAD/2016/Fall/louboutin2016SINBADFhps/louboutin2016SINBADFhps.pdf]\from[url18]

\reference[ref-louboutin2017SINBADFddg]{}%
Louboutin, M., & Herrmann, F. J. (2017a). Data driven gradient sampling
for seismic inversion. SINBAD. Retrieved from
\useURL[url19][https://slim.gatech.edu/Publications/Public/Conferences/SINBAD/2017/Fall/louboutin2017SINBADFddg/louboutin2017SINBADFddg.pdf]\from[url19]

\reference[ref-louboutin2017EAGEess]{}%
Louboutin, M., & Herrmann, F. J. (2017b, June). Extending the search
space of time-domain adjoint-state FWI with randomized implicit time
shifts.
doi:\goto{10.3997/2214-4609.201700831}[url(https://doi.org/10.3997/2214-4609.201700831)]

\reference[ref-louboutin2021ML4SEISMICrla]{}%
Louboutin, M., & Herrmann, F. J. (2021a, November). Randomized linear
algebra for inversion. Retrieved from
\useURL[url20][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2021/louboutin2021ML4SEISMICrla/Tue-10-20-Louboutin.pdf]\from[url20]

\reference[ref-louboutin2021SEGulm]{}%
Louboutin, M., & Herrmann, F. J. (2021b, September). Ultra-low memory
seismic inversion with randomized trace estimation.
doi:\goto{10.1190/segam2021-3584072.1}[url(https://doi.org/10.1190/segam2021-3584072.1)]

\reference[ref-louboutin2022EAGEewi]{}%
Louboutin, M., & Herrmann, F. J. (2022a, June). Enabling wave-based
inversion on GPUs with randomized trace estimation.
doi:\goto{10.3997/2214-4609.202210531}[url(https://doi.org/10.3997/2214-4609.202210531)]

\reference[ref-louboutin2022SEGWSaaa]{}%
Louboutin, M., & Herrmann, F. J. (2022b, September). Abstractions and
algorithms for efficient seismic inversion on accelerators. Retrieved
from
\useURL[url21][https://www.imageevent.org/Workshop/next-fwi-derived-products]\from[url21]

\reference[ref-louboutin2022ML4SEISMIClew]{}%
Louboutin, M., Kartha, Y., Orozco, R., & Herrmann, F. J. (2022,
November). Learned extensions for wave-based simulation and inversion.
Retrieved from
\useURL[url22][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2022/louboutin2022ML4SEISMIClew/index.html]\from[url22]

\reference[ref-louboutin2016ppf]{}%
Louboutin, M., Lange, M., Herrmann, F. J., Kukreja, N., & Gorman, G.
(2017). Performance prediction of finite-difference solvers for
different computer architectures. {\em Computers & Geosciences},
{\em 105}, 148--157.
doi:\useURL[url23][https://doi.org/10.1016/j.cageo.2017.04.014]\from[url23]

\reference[ref-louboutin2017SIAMras]{}%
Louboutin, M., Lange, M., Kukreja, N., Luporini, F., Herrmann, F. J., &
Gorman, G. (2017). Raising the abstraction to separate concerns:
Enabling different physics for geophysical exploration. Retrieved from
\useURL[url24][https://slim.gatech.edu/Publications/Public/Conferences/SIAM/2017/louboutin2017SIAMras/louboutin2017SIAMras_pres.mov]\from[url24]

\reference[ref-louboutin2018dae]{}%
Louboutin, M., Lange, M., Luporini, F., Kukreja, N., Witte, P. A.,
Herrmann, F. J., \ldots{} Gorman, G. J. (2019). Devito (v3.1.0): An
embedded domain-specific language for finite differences and geophysical
exploration. {\em Geoscientific Model Development}.
doi:\goto{10.5194/gmd-12-1165-2019}[url(https://doi.org/10.5194/gmd-12-1165-2019)]

\reference[ref-louboutin2017SINBADFldi]{}%
Louboutin, M., Lange, M., Luporini, F., Kurjeka, N., Hueckelheim, J.,
Gorman, G., \ldots{} Herrmann, F. J. (2017). Latest developments in
devito. SINBAD. Retrieved from
\useURL[url25][https://slim.gatech.edu/Publications/Public/Conferences/SINBAD/2017/Fall/louboutin2017SINBADFldi/louboutin2017SINBADFldi.pdf]\from[url25]

\reference[ref-louboutin2020SCsta]{}%
Louboutin, M., Luporini, F., Witte, P. A., Nelson, R., Bisbas, G.,
Thorbecke, J., \ldots{} Gorman, G. (2020). {\em Scaling through
abstractions high-performance vectorial wave simulations for seismic
inversion with devito} (No. TR-CSE-2020-3). Georgia Institute of
Technology. Retrieved from
\useURL[url26][https://slim.gatech.edu/Publications/Public/TechReport/2020/louboutin2020SCsta/louboutin2020SCsta.html]\from[url26]

\reference[ref-louboutin2015IIPFWIrwi]{}%
Louboutin, M., Peters, B., Smithyman, B. R., & Herrmann, F. J. (2015).
Regularizing waveform inversion by projections onto convex sets.

\reference[ref-louboutin2020SEGtwri]{}%
Louboutin, M., Rizzuti, G., & Herrmann, F. J. (2020a). {\em Time-domain
wavefield reconstruction inversion in a TTI medium} (No. TR-CSE-2020-1).
Georgia Institute of Technology. Retrieved from
\useURL[url27][https://slim.gatech.edu/Publications/Public/TechReport/2020/louboutin2020SEGtwri/louboutin2020SEGtwri.html]\from[url27]

\reference[ref-louboutin2020SIAMTXLAtdw]{}%
Louboutin, M., Rizzuti, G., & Herrmann, F. J. (2020b, October).
Time-domain wavefield reconstruction inversion in tilted transverse
isostropic media. Retrieved from
\useURL[url28][https://slim.gatech.edu/Publications/Public/Conferences/SIAMTXLA/2020/louboutin2020SIAMTXLAtdw/louboutin2020SIAMTXLAtdw_pres.pdf]\from[url28]

\reference[ref-louboutin2021NIPSmcte]{}%
Louboutin, M., Siahkoohi, A., Wang, R., & Herrmann, F. J. (2021).
{\em Low-memory stochastic backpropagation with multi-channel randomized
trace estimation} (No. TR-CSE-2021-1). Retrieved from
\useURL[url29][https://slim.gatech.edu/Publications/Public/TechReport/2021/louboutin2021NIPSmcte/louboutin2021NIPSmcte.pdf]\from[url29]

\reference[ref-louboutin2022RHPCafa]{}%
Louboutin, M., Siahkoohi, A., Yin, Z., Orozco, R., II, T. J. G., Zhang,
Y., \ldots{} Herrmann, F. J. (2022, March). Abstractions for at-scale
seismic inversion. Retrieved from
\useURL[url30][https://slim.gatech.edu/Publications/Public/Conferences/RHPC/2022/louboutin2022RHPCafa/RiceHPC22.pdf]\from[url30]

\reference[ref-louboutin2018SEGeow]{}%
Louboutin, M., Witte, P. A., & Herrmann, F. J. (2018, October). Effects
of wrong adjoints for RTM in TTI media.
doi:\goto{10.1190/segam2018-2996274.1}[url(https://doi.org/10.1190/segam2018-2996274.1)]

\reference[ref-louboutin2017fwi]{}%
Louboutin, M., Witte, P. A., Lange, M., Kukreja, N., Luporini, F.,
Gorman, G., & Herrmann, F. J. (2017). Full-waveform inversion - part 1:
Forward modeling. {\em The Leading Edge}, {\em 36}(12), 1033--1036.
doi:\goto{10.1190/tle36121033.1}[url(https://doi.org/10.1190/tle36121033.1)]

\reference[ref-louboutin2017fwip2]{}%
Louboutin, M., Witte, P. A., Lange, M., Kukreja, N., Luporini, F.,
Gorman, G., & Herrmann, F. J. (2018). Full-waveform inversion - part 2:
Adjoint modeling. {\em The Leading Edge}, {\em 37}(1), 69--72.
doi:\goto{10.1190/tle37010069.1}[url(https://doi.org/10.1190/tle37010069.1)]

\reference[ref-louboutin2022SEGais]{}%
Louboutin, M., Witte, P. A., Siahkoohi, A., Rizzuti, G., Yin, Z.,
Orozco, R., & Herrmann, F. J. (2022, May). Accelerating innovation with
software abstractions for scalable computational geophysics.
doi:\goto{10.1190/image2022-3750561.1}[url(https://doi.org/10.1190/image2022-3750561.1)]

\reference[ref-louboutin2022ML4SEISMICmos]{}%
Louboutin, M., Yin, Z., Orozco, R., II, T. J. G., & Herrmann, F. J.
(2022, November). ML4Seismic open-source software: Updates and
developments. Retrieved from
\useURL[url31][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2022/louboutin2022ML4SEISMICmos/index.html]\from[url31]

\reference[ref-louboutin2020SEGWSspl]{}%
Louboutin, M., Yin, Z., Zhang, Y., & Herrmann, F. J. (2020, October).
Sparsity promoting least-squares migration for long offset sparse OBN.

\reference[ref-luporini2018aap]{}%
Luporini, F., Louboutin, M., Lange, M., Kukreja, N., Witte, P. A.,
Hückelheim, J., \ldots{} Gorman, G. J. (2020). Architecture and
performance of devito, a system for automated stencil computation.
{\em ACM Trans. Math. Softw.}, {\em 46}(1).
doi:\goto{10.1145/3374916}[url(https://doi.org/10.1145/3374916)]

\reference[ref-orozco2022MIDLmei]{}%
Orozco, R., Louboutin, M., & Herrmann, F. J. (2022a). {\em Memory
efficient invertible neural networks for 3D photoacoustic imaging} (No.
TR-CSE-2022-2). Retrieved from
\useURL[url32][https://slim.gatech.edu/Publications/Public/TechReport/2022/orozco2022MIDLmei/midl_2022.html]\from[url32]

\reference[ref-orozco2022ML4SEISMICnfr]{}%
Orozco, R., Louboutin, M., & Herrmann, F. J. (2022b, November).
Normalizing flows for regularization of 3D seismic inverse problems.
Retrieved from
\useURL[url33][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2022/orozco2022ML4SEISMICnfr/index.html]\from[url33]

\reference[ref-orozco2022ML4SEISMICaos]{}%
Orozco, R., Louboutin, M., Siahkoohi, A., Rizzuti, G., & Herrmann, F. J.
(2022, November). Adjoint operators as summary functions in amortized
bayesian inference frameworks. Retrieved from
\useURL[url34][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2022/orozco2022ML4SEISMICaos/index.html]\from[url34]

\reference[ref-peters2015SINBADFrwi]{}%
Peters, B., Smithyman, B. R., Louboutin, M., & Herrmann, F. J. (2015).
Regularizing waveform inversion by projections onto intersections of
convex sets. SINBAD. Retrieved from
\useURL[url35][https://slim.gatech.edu/Publications/Public/Conferences/SINBAD/2015/Fall/peters2015SINBADFrwi/peters2015SINBADFrwi.pdf]\from[url35]

\reference[ref-ren2021AGUsvi]{}%
Ren, Y., Witte, P. A., Siahkoohi, A., Louboutin, M., Yin, Z., &
Herrmann, F. J. (2021, December). Seismic velocity inversion and
uncertainty quantification using conditional normalizing flows.
Retrieved from
\useURL[url36][https://agu.confex.com/agu/fm21/meetingapp.cgi/Paper/815883]\from[url36]

\reference[ref-rizzuti2019SIAMGStwri]{}%
Rizzuti, G., Louboutin, M., Wang, R., Daskalakis, E., & Herrmann, F. J.
(2019a, March). A dual formulation for time-domain wavefield
reconstruction inversion.

\reference[ref-rizzuti2019SEGadf]{}%
Rizzuti, G., Louboutin, M., Wang, R., Daskalakis, E., & Herrmann, F. J.
(2019b, September). A dual formulation for time-domain wavefield
reconstruction inversion.
doi:\goto{10.1190/segam2019-3216760.1}[url(https://doi.org/10.1190/segam2019-3216760.1)]

\reference[ref-rizzuti2020EAGEtwri]{}%
Rizzuti, G., Louboutin, M., Wang, R., & Herrmann, F. J. (2020, January).
Time-domain wavefield reconstruction inversion for large-scale seismics.
Retrieved from
\useURL[url37][https://slim.gatech.edu/Publications/Public/Conferences/EAGE/2020/rizzuti2020EAGEtwri/rizzuti2020EAGEtwri.html]\from[url37]

\reference[ref-rizzuti2020dfw]{}%
Rizzuti, G., Louboutin, M., Wang, R., & Herrmann, F. J. (2021a). A dual
formulation of wavefield reconstruction inversion for large-scale
seismic inversion. {\em Geophysics}, {\em 86}(6), 1ND--Z3.
doi:\goto{10.1190/geo2020-0743.1}[url(https://doi.org/10.1190/geo2020-0743.1)]

\reference[ref-rizzuti2021SIAMGSwrid]{}%
Rizzuti, G., Louboutin, M., Wang, R., & Herrmann, F. J. (2021b, June).
Time-domain wavefield reconstruction inversion for large-scale seismic
inversion. Retrieved from
\useURL[url38][https://slim.gatech.edu/Publications/Public/Conferences/SIAMGS/2021/rizzuti2021SIAMGSwrid/rizzuti2021SIAMGSwrid.pdf]\from[url38]

\reference[ref-rizzuti2021ML4SEISMICdfw]{}%
Rizzuti, G., Louboutin, M., Wang, R., & Herrmann, F. J. (2021c,
November). A dual formulation of wavefield reconstruction inversion for
large-scale seismic inversion. Retrieved from
\useURL[url39][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2021/rizzuti2021ML4SEISMICdfw/Tue-10-55-Rizzuti.pdf]\from[url39]

\reference[ref-sharan2018IEEEIUSspoa]{}%
Sharan, S., Kumar, R., Dumani, D. S., Louboutin, M., Wang, R.,
Emelianov, S., & Herrmann, F. J. (2018, October). Sparsity-promoting
photoacoustic imaging with source estimation.
doi:\goto{10.1109/ULTSYM.2018.8580037}[url(https://doi.org/10.1109/ULTSYM.2018.8580037)]

\reference[ref-siahkoohi2019TRnna]{}%
Siahkoohi, A., Louboutin, M., & Herrmann, F. J. (2019a). {\em Neural
network augmented wave-equation simulation} (No. TR-CSE-2019-1). Georgia
Institute of Technology. Retrieved from
\useURL[url40][https://slim.gatech.edu/Publications/Public/TechReport/2019/siahkoohi2019TRnna/siahkoohi2019TRnna.html]\from[url40]

\reference[ref-siahkoohi2019itl]{}%
Siahkoohi, A., Louboutin, M., & Herrmann, F. J. (2019b). The importance
of transfer learning in seismic modeling and imaging. {\em Geophysics}.
doi:\goto{10.1190/geo2019-0056.1}[url(https://doi.org/10.1190/geo2019-0056.1)]

\reference[ref-siahkoohi2022SEGvcw]{}%
Siahkoohi, A., Louboutin, M., & Herrmann, F. J. (2022, May). Velocity
continuation with fourier neural operators for accelerated uncertainty
quantification.
doi:\goto{10.1190/image2022-3750475.1}[url(https://doi.org/10.1190/image2022-3750475.1)]

\reference[ref-siahkoohi2018SEGcnn]{}%
Siahkoohi, A., Louboutin, M., Kumar, R., & Herrmann, F. J. (2018,
October). Deep convolutional neural networks in prestack seismic-two
exploratory examples.
doi:\goto{10.1190/segam2018-2998599.1}[url(https://doi.org/10.1190/segam2018-2998599.1)]

\reference[ref-siahkoohi2021ML4SEISMICmcn]{}%
Siahkoohi, A., Orozco, R., Rizzuti, G., Witte, P. A., Louboutin, M., &
Herrmann, F. J. (2021a, November). Multifidelity conditional normalizing
flows for physics-guided bayesian inference. Retrieved from
\useURL[url41][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2021/siahkoohi2021ML4SEISMICmcn/Mon-11-45-Siahkoohi.pdf]\from[url41]

\reference[ref-siahkoohi2021EarthMLfar]{}%
Siahkoohi, A., Orozco, R., Rizzuti, G., Witte, P. A., Louboutin, M., &
Herrmann, F. J. (2021b, September). Fast and reliability-aware seismic
imaging with conditional normalizing flows. Retrieved from
\useURL[url42][https://slim.gatech.edu/Publications/Public/Conferences/KAUST/2021/siahkoohi2021EarthMLfar/siahkoohi2021EarthMLfar.pdf]\from[url42]

\reference[ref-siahkoohi2020SIAMTXLAudg]{}%
Siahkoohi, A., Rizzuti, G., Louboutin, M., & Herrmann, F. J. (2020,
October). Unsupervised data-guided uncertainty analysis in imaging and
horizon tracking. Retrieved from
\useURL[url43][https://slim.gatech.edu/Publications/Public/Conferences/SIAMTXLA/2020/siahkoohi2020SIAMTXLAudg/siahkoohi2020SIAMTXLAudg_pres.pdf]\from[url43]

\reference[ref-siahkoohi2021AABIpto]{}%
Siahkoohi, A., Rizzuti, G., Louboutin, M., Witte, P. A., & Herrmann, F.
J. (2021a, January). Preconditioned training of normalizing flows for
variational inference in inverse problems. Retrieved from
\useURL[url44][https://slim.gatech.edu/Publications/Public/Conferences/AABI/2021/siahkoohi2021AABIpto/siahkoohi2020ABIfab.html]\from[url44]

\reference[ref-herrmann2021KAUSTdbi]{}%
Siahkoohi, A., Rizzuti, G., Louboutin, M., Witte, P. A., & Herrmann, F.
J. (2021b, March). Deep bayesian inference for task-based seismic
imaging.

\reference[ref-siahkoohi2020SIAMISsiu]{}%
Siahkoohi, A., Witte, P. A., Louboutin, M., Herrmann, F. J., & Rizzuti,
G. (2020, July). Seismic imaging with uncertainty quantification:
Sampling from the posterior with generative networks. Retrieved from
\useURL[url45][https://slim.gatech.edu/Publications/Public/Conferences/SIAMIS/2020/siahkoohi2020SIAMISsiu/siahkoohi2020SIAMISsiu_pres.pdf]\from[url45]

\reference[ref-yin2022ML4SEISMICavc]{}%
Siahkoohi, A., Yin, Z., Louboutin, M., & Herrmann, F. J. (2022,
November). Amortized velocity continuation with fourier neural
operators. Retrieved from
\useURL[url46][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2022/yin2022ML4SEISMICavc/index.html]\from[url46]

\reference[ref-dasilva2015SINBADFsss]{}%
Silva, C. D., Wason, H., Louboutin, M., Peters, B., Sharan, S., Fang,
Z., & Herrmann, F. J. (2015). Scaling SINBAD software to 3-d on yemoja.
SINBAD. Retrieved from
\useURL[url47][https://slim.gatech.edu/Publications/Public/Conferences/SINBAD/2015/Fall/dasilva2015SINBADFsss/dasilva2015SINBADFsss.pdf]\from[url47]

\reference[ref-wang2017SINBADFnra]{}%
Wang, R., Louboutin, M., Peters, B., Daskalakis, E., & Herrmann, F. J.
(2017). Noise robust and time-domain formulations of wavefield
reconstruction inversion. SINBAD. Retrieved from
\useURL[url48][https://slim.gatech.edu/Publications/Public/Conferences/SINBAD/2017/Fall/wang2017SINBADFnra/wang2017SINBADFnra.pdf]\from[url48]

\reference[ref-witte2016OGHPClst]{}%
Witte, P. A., Louboutin, M., Gorman, G., & Herrmann, F. J. (2017).
{\em A large-scale time-domain seismic modeling and inversion workflow
in julia} (No. TR-EOAS-2017-1). UBC. Retrieved from
\useURL[url49][https://slim.gatech.edu/Publications/Public/TechReport/2017/witte2016OGHPClst/witte2016OGHPClst.pdf]\from[url49]

\reference[ref-witte2015TRoam]{}%
Witte, P. A., Louboutin, M., & Herrmann, F. J. (2015a). {\em Overview on
anisotropic modeling and inversion} (No. TR-EOAS-2015-6). UBC. Retrieved
from
\useURL[url50][https://slim.gatech.edu/Publications/Public/TechReport/2015/witte2015TRoam/witte2015TRoam.html]\from[url50]

\reference[ref-witte2015IIPFWItdf]{}%
Witte, P. A., Louboutin, M., & Herrmann, F. J. (2015b). Time-domain FWI
in TTI media.

\reference[ref-witte2017SINBADFals]{}%
Witte, P. A., Louboutin, M., & Herrmann, F. J. (2017a). A large-scale
framework in julia for fast prototyping of seismic inversion algorithms.
SINBAD. Retrieved from
\useURL[url51][https://slim.gatech.edu/Publications/Public/Conferences/SINBAD/2017/Fall/witte2017SINBADFals/witte2017SINBADFals.pdf]\from[url51]

\reference[ref-witte2017SIAMlsw]{}%
Witte, P. A., Louboutin, M., & Herrmann, F. J. (2017b). Large-scale
workflows for wave-equation based inversion in julia. Retrieved from
\useURL[url52][https://slim.gatech.edu/Publications/Public/Conferences/SIAM/2017/witte2017SIAMlsw/witte2017SIAMlsw_pres.mov]\from[url52]

\reference[ref-witte2019HOTCSEdsagip]{}%
Witte, P. A., Louboutin, M., & Herrmann, F. J. (2019). Domain-specific
abstractions for large-scale geophysical inverse problems. Retrieved
from
\useURL[url53][https://slim.gatech.edu/Publications/Public/Lectures/HotCSE/2019/witte2019HOTCSEdsagip/witte2019HOTCSEdsagip.pdf]\from[url53]

\reference[ref-witte2019RHPCssi]{}%
Witte, P. A., Louboutin, M., Jones, C., & Herrmann, F. J. (2020, March).
Serverless seismic imaging in the cloud. Retrieved from
\useURL[url54][https://slim.gatech.edu/Publications/Public/Conferences/RHPC/2019/witte2019RHPCssi/witte2019RHPCssi.html]\from[url54]

\reference[ref-witte2018alf]{}%
Witte, P. A., Louboutin, M., Kukreja, N., Luporini, F., Lange, M.,
Gorman, G. J., & Herrmann, F. J. (2019a). A large-scale framework for
symbolic implementations of seismic inversion algorithms in julia.
{\em Geophysics}, {\em 84}(3), F57--F71.
doi:\goto{10.1190/geo2018-0174.1}[url(https://doi.org/10.1190/geo2018-0174.1)]

\reference[ref-witte2019ecl]{}%
Witte, P. A., Louboutin, M., Kukreja, N., Luporini, F., Lange, M.,
Gorman, G. J., & Herrmann, F. J. (2019b). Geophysics bright spots:
Efficient coding of large-scale seismic inversion algorithms. {\em The
Leading Edge}, {\em 38}(6), 482--484.
doi:\goto{10.1190/tle38060482.1}[url(https://doi.org/10.1190/tle38060482.1)]

\reference[ref-witte2018fwip3]{}%
Witte, P. A., Louboutin, M., Lensink, K., Lange, M., Kukreja, N.,
Luporini, F., \ldots{} Herrmann, F. J. (2018). Full-waveform inversion -
part 3: optimization. {\em The Leading Edge}, {\em 37}(2), 142--145.
doi:\goto{10.1190/tle37020142.1}[url(https://doi.org/10.1190/tle37020142.1)]

\reference[ref-witte2018cls]{}%
Witte, P. A., Louboutin, M., Luporini, F., Gorman, G. J., & Herrmann, F.
J. (2019a). Compressive least-squares migration with on-the-fly fourier
transforms. {\em Geophysics}, {\em 84}(5), R655--R672.
doi:\goto{10.1190/geo2018-0490.1}[url(https://doi.org/10.1190/geo2018-0490.1)]

\reference[ref-witte2019SIAMCSEclsmft]{}%
Witte, P. A., Louboutin, M., Luporini, F., Gorman, G. J., & Herrmann, F.
J. (2019b, March). Compressive least squares migration with on-the-fly
fourier transforms.

\reference[ref-witte2019SEGedw]{}%
Witte, P. A., Louboutin, M., Modzelewski, H., Jones, C., Selvage, J., &
Herrmann, F. J. (2019, September). Event-driven workflows for
large-scale seismic imaging in the cloud.
doi:\goto{10.1190/segam2019-3215069.1}[url(https://doi.org/10.1190/segam2019-3215069.1)]

\reference[ref-witte2019TPDedas]{}%
Witte, P. A., Louboutin, M., Modzelewski, H., Jones, C., Selvage, J., &
Herrmann, F. J. (2020). An event-driven approach to serverless seismic
imaging in the cloud. {\em IEEE Transactions on Parallel and Distributed
Systems}, {\em 31}(9), 2032--2049.
doi:\goto{10.1109/TPDS.2020.2982626}[url(https://doi.org/10.1109/TPDS.2020.2982626)]

\reference[ref-witte2021JULIACONmedlj]{}%
Witte, P. A., Louboutin, M., Siahkoohi, A., Rizzuti, G., Peters, B., &
Herrmann, F. J. (2021, July). InvertibleNetworks.jl - memory efficient
deep learning in julia. Retrieved from
\useURL[url55][https://slim.gatech.edu/Publications/Public/Conferences/JuliaCon/2021/witte2021JULIACONmedlj/witte2021JULIACONmedlj.pdf]\from[url55]

\reference[ref-witte2015IIPFWIspl]{}%
Witte, P. A., Tu, N., Esser, E., Yang, M., Louboutin, M., & Herrmann, F.
J. (2015). Sparsity-promoting least-square migration with linearized
bregman and compressive sensing.

\reference[ref-yin2022ML4SEISMICsfg]{}%
Yin, Z., Erdinc, H. T., Gahlot, A. P., Louboutin, M., & Herrmann, F. J.
(2022, November). Simulation-based framework for geological carbon
storage monitoring. Retrieved from
\useURL[url56][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2022/yin2022ML4SEISMICsfg/index.html]\from[url56]

\reference[ref-yin2022TLEdgc]{}%
Yin, Z., Erdinc, H. T., Gahlot, A. P., Louboutin, M., & Herrmann, F. J.
(2023). Derisking geological carbon storage from high-resolution
time-lapse seismic to explainable leakage detection. {\em The Leading
Edge}, {\em 42}(1), 6976.
doi:\goto{10.1190/tle42010069.1}[url(https://doi.org/10.1190/tle42010069.1)]

\reference[ref-yin2021ML4SEISMICism]{}%
Yin, Z., Louboutin, M., & Herrmann, F. J. (2021a, November). Improved
seismic monitoring of CO2 sequestration with the weighted joint recovery
model. Retrieved from
\useURL[url57][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2021/yin2021ML4SEISMICism/Tue-11-20-Yin.html]\from[url57]

\reference[ref-yin2021SEGcts]{}%
Yin, Z., Louboutin, M., & Herrmann, F. J. (2021b, September).
Compressive time-lapse seismic monitoring of carbon storage and
sequestration with the joint recovery model.
doi:\goto{10.1190/segam2021-3569087.1}[url(https://doi.org/10.1190/segam2021-3569087.1)]

\reference[ref-yin2022TRANSFORMjulia]{}%
Yin, Z., Louboutin, M., Witte, P. A., Siahkoohi, A., Rizzuti, G.,
Orozco, R., \ldots{} Herrmann, F. J. (2022, April). Julia for
geoscience. Retrieved from
\useURL[url58][https://transform.softwareunderground.org/2022-julia-for-geoscience]\from[url58]

\reference[ref-yin2022ML4SEISMICutc]{}%
Yin, Z., Orozco, R., Siahkoohi, A., Louboutin, M., & Herrmann, F. J.
(2022, November). Uncertainty-aware time-lapse CO$_2$ monitoring with
learned end-to-end inversion. Retrieved from
\useURL[url59][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2022/yin2022ML4SEISMICutc/index.html]\from[url59]

\reference[ref-yin2020SEGesi]{}%
Yin, Z., Orozco, R., Witte, P. A., Louboutin, M., Rizzuti, G., &
Herrmann, F. J. (2020, September). Extended source imaging - a unifying
framework for seismic and medical imaging.
doi:\goto{10.1190/segam2020-3426999.1}[url(https://doi.org/10.1190/segam2020-3426999.1)]

\reference[ref-yin2022SEGlci]{}%
Yin, Z., Siahkoohi, A., Louboutin, M., & Herrmann, F. J. (2022, May).
Learned coupled inversion for carbon sequestration monitoring and
forecasting with fourier neural operators.
doi:\goto{10.1190/image2022-3722848.1}[url(https://doi.org/10.1190/image2022-3722848.1)]

\reference[ref-zhang2022SEGass]{}%
Zhang, Y., Louboutin, M., Siahkoohi, A., Yin, Z., Kumar, R., & Herrmann,
F. J. (2022, May). A simulation-free seismic survey design by maximizing
the spectral gap.
doi:\goto{10.1190/image2022-3751690.1}[url(https://doi.org/10.1190/image2022-3751690.1)]

\reference[ref-zhang2022ML4SEISMICtss]{}%
Zhang, Y., Louboutin, M., Siahkoohi, A., Yin, Z., Kumar, R., Lopez, O.,
& Herrmann, F. J. (2022, November). Time-lapse seismic survey design by
maximizing the spectral gap. Retrieved from
\useURL[url60][https://slim.gatech.edu/Publications/Public/Conferences/ML4SEISMIC/2022/zhang2022ML4SEISMICtss/index.html]\from[url60]

\reference[ref-zhang2023otl]{}%
Zhang, Y., Yin, Z., Lopez, O., Siahkoohi, A., Louboutin, M., Kumar, R.,
& Herrmann, F. J. (2023, January). {\em Optimized time-lapse acquisition
design via spectral gap ratio minimization}. Retrieved from
\useURL[url61][https://slim.gatech.edu/Publications/Public/Submitted/2023/zhang2023otl/Spectral_Gap_Paper.html]\from[url61]

\stopcslreferences
\stopsectionlevel

\stoptext
